Introducing ICBe: Supplementary Information

### 2024-06-16 replication_paper/psrm_draft/ICBe_supplemental_information.tex
pre-pull

>>>>

\begin{verbatim}
## Warning: package 'googlesheets4' was built under R version 4.3.1
\end{verbatim}

\begin{verbatim}
## Warning: package 'tidyverse' was built under R version 4.2.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'tibble' was built under R version 4.3.1
\end{verbatim}

\begin{verbatim}
## Warning: package 'tidyr' was built under R version 4.3.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'readr' was built under R version 4.3.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'purrr' was built under R version 4.3.1
\end{verbatim}

\begin{verbatim}
## Warning: package 'dplyr' was built under R version 4.3.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'stringr' was built under R version 4.3.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'forcats' was built under R version 4.2.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'lubridate' was built under R version 4.3.1
\end{verbatim}

\begin{verbatim}
## Warning: package 'rvest' was built under R version 4.2.1
\end{verbatim}
